Advantages of mixed unitary operators for quantum information processing

### 2019-01-11 decorrelation/mixed_unitaries.tex
moving sections around

Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel. Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed. The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits. However, it is not the only optimization target that can be chosen. If the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic. Using a constrained numerical optimization routine, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}. Indeed, this is the approach we consider in our experimental implementation in Section \ref{sec:experimental_results}. More generally, as we will discuss, there are a number of options one may wish to consider when selecting weights to prepare a mixed unitary process.

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\subsection{A Simple Example}
\label{sec:simple_example}
Before discussing how to produce MUPs with desirable qualities, we will give a simple example demonstrating the merits of different approaches to producing MUPs. There are often many possible ways of implementing any given target quantum gate. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.  As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

\begin{center}

\begin{tabular}{cccc}
	Gate & $H_{\rm{eff}}$ & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
\hline
	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
\end{tabular}

\end{center}

In this case, the MUP that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will a linear dependence on $\epsilon$. On the otherhand, any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$.

In both cases it is clear that we should select the gates with smaller error, i.e. $\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error. Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter. \cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to. We will discuss numerical approaches to solving this Section \ref{sec:norm}.

Another interesting property of the MUP given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift. In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways. Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$. In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order. Given these considerations from this simple example, we will now consider a numerical strategy for generating MUPs.
\subsection{Diamond Norm Minimization}
\label{sec:small_diamond_norm}
As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MUP with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. Such a problem forms what is known as a convex optimization problem, and can be written with the following shorthand:

@@

where we write the contraints on the variable to be optimized over below the objective, and we write the cost function on the right. Linearly constrained minimization problems with quadratic cost functions like this have been proveb to be efficiently solvable by methods like the Elipsoid Method\needcite, however these have very poor average case performance. However, there are many existing convex solver software packages that solve these problems efficiently in practice, with some formal proofs showing runtimes as good as $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
\subsection{Robustly Mixed Unitary Processes}
\label{sec:robustly_mixed}

@@

@@

\begin{equation}\label{eq:minimization_l2}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation}
with $\eta \geq 0$. By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor. The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.

@@

\begin{equation}\label{eq:minimization_regularization}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}^T\omega|| + t\\
&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation} with $\lambda\geq0$. As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be. For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.

% ==============================================================================
% Section: Numerical Results
% ==============================================================================
\section{Numerical Results}
\label{sec:numerical_results}
\label{one_qubit_performance}
In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
\begin{equation}\label{eq:1Qham}
  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls. In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$. We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal. Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMUP}. These results demonstrate several properties that make MUPs both useful and tractable.

First, naively generating a 0MUP results in nontrivial support on all the members of the control family. However, by rewriting the minimization to impose the sparsity constraint discussed in Section \ref{sec:robustly_mixed}, we can generate a 0MUP that uses just five of the controls. This shows that through adding constraints to our optimization routine, we can make the MUP practically useful. In both cases we impose the same $\ell_2$ penalty as described in Section \ref{sec:robustly_mixed}, so that the algorithm preferentially selects controls with smaller errors. Imposing this constraint allows us to trade off flatness at the origin for performance.
\subsection{Two Qubit Performance Analysis}
\label{two_qubit_performance}
In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:
\begin{equation} \label{eq:2Qham}
\begin{split}
H(\vec{\delta}, \vec{\epsilon}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
&+ \frac{1}{10}(XX + YY)
\end{split}
\end{equation}

%\begin{figure}
%  \centering
%  \includegraphics[width=\columnwidth]{bangbang.png}
%  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the unused $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
%  \label{fig:bangbang}
%\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction. Shown with lower alpha values are example constituent controls. The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin. For all detuning values the 1MUP performs as well or better than the 0MUP. When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm. Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
  \label{fig:2MUP}
\end{figure}
% ==============================================================================
% Section: Experimental Results
% ==============================================================================

\section{Experimental Results}
\label{sec:experimental_results}
Here we present experimental results from implementing our routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{rb_data.pdf}
  \caption{Randomized benchmarking experiments ran using different pulse definitions. The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the MUP.}
  \label{fig:rb}
\end{figure}

As discussed in Section \ref{sec:robustly_mixed}, we chose here to minimize the off diagonal elements of the process matrix. To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process. We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$. In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses. In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors. The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$. Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.

Additionally, by minimizing the off-diagonal elements of the process matrix, rather than balancing the Hamiltonian errors, we expect to produce a process with minimal coherent error in the absence of drift. To see that this is the case, we cite the results in \cite{Ball2016}. For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length. On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length. We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables. Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.

@@

In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization. While performing a complete optimization in this way would require full process tomography, one could intead optimize via partial tomography. By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.

% ==============================================================================
% Section: Acknowledgements
% ==============================================================================
\section{Acknowledgements}
\label{sec:acknowledgements}
Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
\bibliography{decorrelation.bib}

>>>>

Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel. Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed. The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits. However, it is not the only optimization target that can be chosen.

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\subsection{Simple Example}
\label{sec:simple_example}
There are often many possible ways of implementing any given target quantum gate. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} As a simple example, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

\begin{center}
\begin{tabular}{cccc}
	Gate & $H_{\rm{eff}}$ & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
\hline
	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
\end{tabular}
\end{center}

In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic. Such a channel could be constructed, for instance, by drawing from this collection uniformly at random. More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}. We implemented such a routine on a superconducting qubit.
% ==============================================================================
% Section: Experimental Results
% ==============================================================================

\subsection{Experimental Implementation}
\label{sec:experimental_results}
Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.

As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix. To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process. We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$. In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses. In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors. The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$. Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses. 
\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{rb_data.pdf}
  \caption{Randomized benchmarking experiments ran using different pulse definitions. The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the MUP.}
  \label{fig:rb}
\end{figure}

Additionally, by minimizing the off-diagonal elements of the process matrix, we expect to produce a process with minimal coherent error. To see that this is the case, we cite the results in \cite{Ball2016}. For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length. On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length. We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables. Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.

\subsection{Diamond Norm Minimization}
\label{sec:small_diamond_norm}
If our primary goal is for our MUP to have increased performance, then a useful target for constructing MUPs is instead minimizing the diamond norm. As in Section \ref{sec:simple_example}, the MUP that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$. Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$. While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application. However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MUP with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. This forms a convex optimization problem, and can be written as:

@@

Linearly constrained minimization problems with quadratic cost functions like this have been proven to be efficiently solvable by methods like the Elipsoid Method\needcite, however these have very poor average case performance. However, there are many existing convex solver software packages that solve these problems efficiently in practice, with some formal proofs showing runtimes as good as $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.

%In both cases it is clear that we should select the gates with smaller error, i.e. $\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error. Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter. \cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to. We will discuss numerical approaches to solving this Section \ref{sec:norm}.

%Another interesting property of the MUP given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift. In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways. Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$. In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order. Given these considerations from this simple example, we will now consider a numerical strategy for generating MUPs.

\subsection{Robustly Mixed Unitary Processes}
\label{sec:robustly_mixed}

@@

% ==============================================================================
% Section: Numerical Results
% ==============================================================================
\subsection{Numerical Implementation}
\label{sec:numerical_results}
\label{one_qubit_performance}
In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
\begin{equation}\label{eq:1Qham}
  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls. In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$. We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal. Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMUP}. These results demonstrate several properties that make MUPs both useful and tractable.

In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:
\begin{equation} \label{eq:2Qham}
\begin{split}
H(\vec{\delta}, \vec{\epsilon}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
&+ \frac{1}{10}(XX + YY)
\end{split}
\end{equation}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction. Shown with lower alpha values are example constituent controls. The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin. For all detuning values the 1MUP performs as well or better than the 0MUP. When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm. Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
  \label{fig:2MUP}
\end{figure}

@@

\begin{equation}\label{eq:minimization_l2}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation}
with $\eta \geq 0$. By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor. The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$. Naively generating the 1Q 0MUP in the previous section results in nontrivial support on all the members of the control family. However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MUP uses just five of the controls. This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.

@@

\begin{equation}\label{eq:minimization_regularization}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}^T\omega|| + t\\
&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation} with $\lambda\geq0$. As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be. For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
In both the 0MUP and the 1MUP case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors. Adding this constrain made the 0MUP perform better at the origin by nearly an order of magnitude, and moved the 1MUP from being out-performed by the 0MUP for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls. Imposing this constraint allows us to trade off flatness at the origin for performance.

@@

In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization. While performing a complete optimization in this way would require full process tomography, one could intead optimize via partial tomography. By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
% ==============================================================================
% Section: Acknowledgements
% ==============================================================================

\section{Acknowledgements}
\label{sec:acknowledgements}
Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
\bibliography{decorrelation.bib}
